Democracy, Public Support, and Measurement Uncertainty

### 2021-06-29 paper/dcpo_demsupport.Rmd

# Removed the comments for the final replication file
## Claasseen and extend data

# osf_retrieve_file("hczmf") %>% 
#     osf_download(path = "../data")
# 
# osf_retrieve_file("wbu6m") %>% 
#     osf_download(path = "../data")
# 
# osf_retrieve_file("2jhbc") %>% 
#     osf_download(path = "../data")
# 
# osf_retrieve_file("u96m8") %>% 
#     osf_download(path = "../data")

@@

```{r cls-pointAJPS}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

```{r cls-modelAJPS}

@@

```{r cls-uncertainAJPSfull}
result_clsUncertainFull <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

names(result_clsUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_clsUncertainFull, file = here::here("output", "estimates_clsAJPSfullUncertain.RDS"))
```

```{r dcpo-modelAJPS}
#ls_iv <- c("plm::lag(theta, 1)", 
#    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")

ls_iv <- c("plm::lag(theta_trim, 1)", 
    "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") #use trimmed data

ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)")

ls_mod_ajpsDCPO <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
    )
)
```

```{r dcpo-uncertainAJPSfull}
result_dcpoUncertainFull <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

names(result_dcpoUncertainFull) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_dcpoUncertainFull, file = here::here("output", "estimates_dcpoAJPSfullUncertain.RDS"))
```

```{r coefName-AJPS, eval=TRUE}
index_coefName <- c(
  `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
  `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
  `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
  `plm::lag(theta_trim, 1)` = "Support[t-1]",
  `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
  `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
  `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
  `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
  `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
  `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
)
```

@@

result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))

type_model <-
  c("Claassen 2019", "Claassen Uncertainty", "DCPO Uncertainty")

result_ajpsPooled <-
  list(result_cls,
       result_clsUncertainFull,
       result_dcpoUncertainFull) %>%
  map2_df(type_model, ~ {
    .x$pooled[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_ajpsRegime <-
  list(result_cls,
       result_clsUncertainFull,
       result_dcpoUncertainFull) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

@@

```{r cls-pointAPSR}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

```{r cls-modelAPSR}
ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")

@@

```{r cls-uncertainAPSRfull}
result_clsFullUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

names(result_clsFullUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_clsFullUncertainAPSR, file = here("output", "estimates_clsFullUncertainAPSR.RDS"))
```

```{r dcpo-modelAPSR}
ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")

ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

ls_ivFD <- c("Vdem_libdem_z",
             "Vdem_polyarchy_z + Vdem_liberal_z")

ls_ctrlFD <- c("", " + corruption_z")

ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

ls_mod_apsrDCPO <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)
```

```{r dcpo-uncertainAPSRfull}
result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
})

names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_dcpoUncertainAPSR, file = here("output", "estimates_dcpoUncertainAPSR.RDS"))
```

@@

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", fig.width=7, fig.height=10, eval = TRUE}
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))

@@

result_apsrPooled <-
  list(result_clsAPSR,
       result_clsFullUncertainAPSR,
       result_dcpoUncertainAPSR) %>%
  map2_df(type_model, ~ {
    .x$pooled1[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_apsrRegime <-
  list(result_clsAPSR,
       result_clsFullUncertainAPSR,
       result_dcpoUncertainAPSR) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime1`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

@@

```{r num-cls2020a, results='asis'}
tb_result_cls <- map(result_cls, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)

@@

```{r num-cls2020aUncertain, results='asis'}
tb_result_clsUncertain <- map(result_clsUncertain, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

names_coef <- c(
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(theta, 1)" = "Support[t-1]",
  "plm::lag(theta_dem, 1)" = "Support in Democracy",
  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)

modelsummary(tb_result_clsUncertain, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-cls2020aDCPO, results='asis'}
tb_result_DCPO <- map(result_dcpoUncertain, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

names(tb_result_DCPO) <- c("Pooled", "Pooled-Regime", 
                          "GMM", "GMM-Regime")

names_coef <- c(
  "plm::lag(Vdem_libdem, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Vdem_libdem, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(theta, 1)" = "Support[t-1]",
  "plm::lag(theta_dem, 1)" = "Support in Democracy",
  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
  "plm::lag(lg_imp_mdpgdp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(mdprgdp_grwth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Region_libdem, 1)" = "Regional~democracy[t-1]",
  "plm::lag(muslism_prop_2010, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(dependence_pc_di, 1)" = "Resource~dependence[t-1]"
)

modelsummary(tb_result_DCPO, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-cls2020b, results='asis'}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)

@@

```{r num-cls2020bUncertain, results='asis'}
tb_result_clsUncertainAPSR <- map(result_clsUncertainAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)

modelsummary(tb_result_clsUncertainAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-cls2020bDCPO, results='asis'}
tb_result_dcpoAPSR <- map(result_dcpoAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(theta, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(theta, 1:2)2" = "Democratic\n Mood\n (t-2)",

  "diff(Vdem_libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Vdem_libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Vdem_libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",

  "diff(Vdem_polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Vdem_polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Vdem_polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Vdem_liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Vdem_liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Vdem_liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lg_imp_mdpgdp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lg_imp_mdpgdp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lg_imp_mdpgdp, 1)" = "Log GDP\n (t-1)",
  "diff(corruption_z, lag = 1)" = "Corruption\n (Difference)",
  "corruption_z" = "Corruption\n (Difference)",
  "plm::lag(corruption_z, 1)" = "Corruption\n (t-1)"
)

modelsummary(tb_result_dcpoAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r datawitherrors}

ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

df_cls_errors <- purrr::map(1:900, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>%
    reformat_dcpo_output("theta")  %>%
    mutate(iter = anEntry) 
  }
  )

cls_theta_uncertainty <- bind_rows(df_cls_errors)
saveRDS(cls_theta_uncertainty,"data/cls_theta_uncertainty.rds")

ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpo <- purrr::map_df(1:900, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>%
    reformat_dcpo_output("theta") %>%
    mutate(iter = anEntry) %>%
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country"))
})

saveRDS(df_dcpo,"dcpo_theta_uncertainty.rds")

>>>>

# Removed the comments for the final replication file
## Claasseen and extend data
# 
# osf_retrieve_file("hczmf") %>%
#     osf_download(path = "../data")
# 
# osf_retrieve_file("wbu6m") %>%
#     osf_download(path = "../data")
# 
# osf_retrieve_file("2jhbc") %>%
#     osf_download(path = "../data")
# 
# osf_retrieve_file("u96m8") %>%
#     osf_download(path = "../data", conflicts = "overwrite")

@@

```{r pointAJPS}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

```{r model-AJPS}

@@

```{r result-pureAJPS}
result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(pure_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

names(result_pureAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_pureAJPS, file = here::here("output", "estimates_clsPureAJPS.RDS"))
```

```{r result-expAJPS}
result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(exp_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

names(result_expAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_expAJPS, file = here::here("output", "estimates_clsExpAJPS.RDS"))
```

```{r coefName-AJPS, eval=TRUE}
index_coefName <- c(
  `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
  `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
  `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
  `plm::lag(theta, 1)` = "Support[t-1]",
  `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
  `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
  `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
  `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
  `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
  `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
)
```

@@

result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))

type_model <-
  c("Original", "Uncertainty", "Uncertainty+Expanded Data")

result_ajpsPooled <-
  list(result_cls,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$pooled[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_ajpsRegime <-
  list(result_cls,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

@@

```{r pointAPSR}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

```{r model-APSR}
ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")

@@

```{r result-pureAPSR}
result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(pure_cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

names(result_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_pureAPSR, file = here("output", "estimates_clsPureAPSR.RDS"))
```

```{r result-expAPSR}
result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(exp_cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

  result_expAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
})

names(result_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_expAPSR, file = here("output", "estimates_clsExpAPSR.RDS"))
```

@@

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", fig.width=7, fig.height=10, eval = TRUE}
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_pureAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))

@@

result_apsrPooled <-
  list(result_clsAPSR,
       result_pureAPSR,
       result_expAPSR) %>%
  map2_df(type_model, ~ {
    .x$pooled1[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_apsrRegime <-
  list(result_clsAPSR,
       result_pureAPSR,
       result_expAPSR) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime1`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

@@

```{r num-labelAJPS}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)
```

```{r num-pointAJPS, results='asis'}
tb_result_cls <- map(result_cls, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

@@

```{r num-pureAJPS, results='asis'}
tb_result_pureAJPS <- map(result_pureAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

modelsummary(tb_result_pureAJPS, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-expAJPS, results='asis'}
tb_result_expAJPS <- map(result_expAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

names(tb_result_expAJPS) <- c("Pooled", "Pooled-Regime", 
                          "GMM", "GMM-Regime")

modelsummary(tb_result_expAJPS, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-labelAPSR}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)
```

```{r num-pointAPSR, results='asis'}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

@@

```{r num-pureAPSR, results='asis'}
tb_result_pureAPSR <- map(result_pureAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_pureAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

modelsummary(tb_result_pureAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-expAPSR, results='asis'}
tb_result_expAPSR <- map(result_expAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_expAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

modelsummary(tb_result_expAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@
